---
title: "Untitled"
output: html_document
date: "2023-02-09"
---

```{r}
setwd("C:/Users/lrawl/OneDrive/Documents/Data Analytics/5956")
#Gathering Data
Globalhealthdata <- read.csv("~/Data Analytics/5956/IntOrg_NCD_variables_2022_02_02.csv")
```

```{r}
library(ggplot2)
library(dplyr)
library(caret)
library(tidyr)
#Looking at the first few rows of the data
head(Globalhealthdata)
-----------------------------------------------------------------------------------
#Creating sample
set.seed(38)
n <- nrow(Globalhealthdata)
index_selected <- sample(1:n, size = 3000, replace = TRUE)
Global_sample1 <- Globalhealthdata[index_selected, ]
#Getting rid of N/A's
Global_sample <- na.omit(Global_sample1)
View(Global_sample)
#Counting number of N/A's in each column
sapply(Global_sample, function(x) sum(is.na(x)))
```

## Weight and Obesity in Adults

```{r}
#Looking at obesity in sample
library(ggplot2)
ggplot(data = Global_sample)+ geom_histogram(mapping = aes(x = Prevalence_obesity_adults))+ labs(x="Prevalence of Obesity in Adults", y="Frequency", title = "Histogram of the Prevalence of Obesity in Adults")
```

Looking at this histograms shows that low prevalence of obesity is most common in the sample.

```{r}
#Looking at correlation between underweight adults and sex
library(ggplot2)
ggplot(data = Global_sample, mapping = aes(x = Prevalence_underweight_adults, colour = Sex)) +
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Graph showing the Prevalence of Underweight Adults")

```

We can see from this graph that more males from around the world are underweight than females.

```{r}
#Looking at correlation between underweight adults and superrregion
library(ggplot2)
ggplot(data = Global_sample, mapping = aes(x = Prevalence_underweight_adults, colour = Superregion)) +
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Prevalence of Underweight Adults by Superregion")
```

This graph shows a high prevalence of underweight adults in sub-saharan Africa and South Asia. Central and Eastern Europe, high-income Western countries, and high-income Asian Pacific countries have lower prevalence of underweight adults.

```{r}
#Correlation between morbidly obese adults and superregion
ggplot(data = Global_sample, mapping = aes(x = Prevalence_morbid_obesity_adults, colour = Superregion)) +
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Morbidly Obese Adults",title = "Prevelence of Morbidly Obese Adults in Differing Superregions", y="Frequency")
```

This graph shows a high prevalence of morbidly obese adults in Oceania and low prevalence in Sub-Saharan Africa.



## Results and Conclusions

```{r}
#Looking at correlation between underweight adults and super region
library(ggplot2)
ggplot(data = scaled_data, mapping = aes(x = Prevalence_underweight_adults, colour = factor(cluster))) +scale_color_discrete(name = "Cluster")+
  geom_freqpoly(binwidth = 0.005)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Prevalence of Underweight Adults by Cluster")
```
This graph shows that cluster 2 has the lowest prevalence of underweight adults. Cluster 4 has the highest prevalence of underweight adults.


```{r}
ggplot(data = scaled_data, mapping = aes(x = Prevalence_obesity_adults, colour = factor(cluster))) +scale_color_discrete(name = "Cluster")+
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Obesity in Adults", y="Frequency", title="Prevalence of Obesity in Adults by Cluster")
```
Cluster 4 has the highest frequency for the lowest of obesity in adults. Cluster 2 and 1 have higher prevalences around the 0.2 mark.

```{r}
ggplot(data = scaled_data, mapping = aes(x = Prevalence_morbid_obesity_adults, colour = factor(cluster))) +scale_color_discrete(name = "Cluster")+
  geom_freqpoly(binwidth = 0.005)+labs(x="Prevalence of Morbid Obesity in Adults", y="Frequency", title="Prevalence of Morbid Obesity in by Cluster")
```
Cluster 4 has the highest frequency of low prevalence of morbid obesity in adults, whereas cluster 3 has the lowest frequency of low prevalence. 

```{r}
#Comparing obesity and weight
library(GGally)
scaled_data$cluster<-as.character(scaled_data$cluster)
ggpairs(scaled_data,                 # Data frame
        columns = 6:8,        # Columns
        aes(color = scaled_data$cluster,  # Color by group 
            alpha = 0.5))
```

