---
title: "Untitled"
output: html_document
date: "2023-02-09"
---

```{r}
setwd("C:/Users/lrawl/OneDrive/Documents/Data Analytics/5956")
#Gathering Data
Globalhealthdata <- read.csv("~/Data Analytics/5956/IntOrg_NCD_variables_2022_02_02.csv")
```

```{r}
#Looking at the first few rows of the data
head(Globalhealthdata)
-----------------------------------------------------------------------------------
#Creating sample
set.seed(38)
n <- nrow(Globalhealthdata)
index_selected <- sample(1:n, size = 3000, replace = TRUE)
Global_sample <- Globalhealthdata[index_selected, ]

```

## Weight and Obesity in Adults

```{r}
#Looking at obesity in sample
library(ggplot2)
ggplot(data = Global_sample)+ geom_histogram(mapping = aes(x = Prevalence_obesity_adults))+ labs(x="Prevalence of Obesity in Adults", y="Frequency", title = "Histogram of the Prevalence of Obesity in Adults")
```

Looking at this histograms shows that low prevalence of obesity is most common in the sample.

```{r}
#Looking at correlation between underweight adults and sex
library(ggplot2)
ggplot(data = Global_sample, mapping = aes(x = Prevalence_underweight_adults, colour = Sex)) +
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Graph showing the Prevalence of Underweight Adults")

```

We can see from this graph that more males from around the world are underweight than females.

```{r}
#Looking at correlation between underweight adults and superrregion
library(ggplot2)
ggplot(data = Global_sample, mapping = aes(x = Prevalence_underweight_adults, colour = Superregion)) +
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Prevalence of Underweight Adults by Superregion")
```

This graph shows a high prevalence of underweight adults in sub-saharan Africa and South Asia. Central and Eastern Europe, high-income Western countries, and high-income Asian Pacific countries have lower prevalence of underweight adults.

```{r}
#Correlation between morbidly obese adults and superregion
ggplot(data = Global_sample, mapping = aes(x = Prevalence_morbid_obesity_adults, colour = Superregion)) +
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Morbidly Obese Adults",title = "Prevelence of Morbidly Obese Adults in Differing Superregions", y="Frequency")
```

This graph shows a high prevalence of morbidly obese adults in Oceania and low prevalence in Sub-Saharan Africa.

##IGNORE

```{r}
library(caret)
set.seed(38)
trainIndex <- createDataPartition(Globalhealthdata$Sex,
p = 2/3,
list = FALSE,
times = 1)
global_train <- Globalhealthdata[ trainIndex, ]
global_test <- Globalhealthdata[-trainIndex, ]
```

## Including Plots

```{r pressure, echo=FALSE}
glm_mod <- train(
form = sex ~ ,
data = Globalhealthdata,
method = "glmStepAIC",
family = "binomial")
saveRDS(glm_mod,
"glm_mod.rds")
glm_mod <- readRDS("glm_mod.rds")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Results and Conclusions

```{r}
#Looking at correlation between underweight adults and superrregion
library(ggplot2)
ggplot(data = scaled_data, mapping = aes(x = Prevalence_underweight_adults, colour = factor(cluster))) +scale_color_discrete(name = "Cluster")+
  geom_freqpoly(binwidth = 0.005)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Prevalence of Underweight Adults by Cluster")
```

```{r}
ggplot(data = scaled_data, mapping = aes(x = Prevalence_obesity_adults, colour = factor(cluster))) +scale_color_discrete(name = "Cluster")+
  geom_freqpoly(binwidth = 0.01)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Prevalence of Underweight Adults by Cluster")
```

```{r}
ggplot(data = scaled_data, mapping = aes(x = Prevalence_morbid_obesity_adults, colour = factor(cluster))) +scale_color_discrete(name = "Cluster")+
  geom_freqpoly(binwidth = 0.005)+labs(x="Prevalence of Underweight Adults", y="Frequency", title="Prevalence of Underweight Adults by Cluster")
```
